---
title: "Costa Final Project"
author: "Leo Costa"
date: "11/20/2021"
output: html_document
---

```{r, include = false}
library(tidyverse)
library(dplyr)
library(haven)
library(parsnip)
library(nnet)

NSL <- read_sav("NSL.sav")
#View(NSL)
#names(NSL)
```

Univariate Analyses: Predictor Variables: Citizenship Status
```{r}
summary(NSL$qn9)
table(NSL$qn9)
NSL$qn9[is.na(NSL$qn9)] <- 3
NSL$qn9[NSL$qn9 == 9] <- NA

NSL$qn9 <- as.factor(NSL$qn9)
levels(NSL$qn9)[levels(NSL$qn9)=="1"] <- "Naturalized Citizen"
levels(NSL$qn9)[levels(NSL$qn9)=="2"] <- "Non-citizen"
levels(NSL$qn9)[levels(NSL$qn9)=="3"] <- "Natural Born Citizen"

table(NSL$qn9)
prop.table(table(NSL$qn9))

ggplot(NSL, aes(qn9)) + 
  geom_bar() + 
  labs(title = "Citizenship Status", subtitle = "Are you a citizen of the United States?", x = "Response", y = "Count")
```

Univariate Analyses: Predictor Variables: English Language Proficiency
lower numbers correspond to lower proficiency
```{r}
table(NSL$qnlan3) 

NSL$qnlan3 <- as.factor(NSL$qnlan3)
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="1"] <- "Proficient" #Very well
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="2"] <- "Proficient" #Pretty well
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="3"] <- "Not proficient" #Just a little
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="4"] <- "Not proficient" #Not at all
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="8"] <- NA
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="9"] <- NA # 8: 2, 9: 3

summary(NSL$qnlan3)
prop.table(table(NSL$qnlan3))

ggplot(NSL, aes(qnlan3)) +
  geom_bar()
```

Univariate Analyses: Predictor Variables: Experiences of Discrimination - right skew
```{r}
NSL$qn23c[NSL$qn23c == 2] <- 0
NSL$qn23d[NSL$qn23d == 2] <- 0
NSL$qn23e[NSL$qn23e == 2] <- 0
NSL$qn23f[NSL$qn23f == 2] <- 0

table(NSL$qn23c) #8: 2 values
table(NSL$qn23d) #8: 2 values
table(NSL$qn23e) #8: 2 values; 9: 2 values 
table(NSL$qn23f) #8: 9 values; 9: 4 values
NSL$qn23c[NSL$qn23c == 8 | NSL$qn23c == 9] <- NA
NSL$qn23d[NSL$qn23d == 8 | NSL$qn23d == 9] <- NA
NSL$qn23e[NSL$qn23e == 8 | NSL$qn23e == 9] <- NA
NSL$qn23f[NSL$qn23f == 8 | NSL$qn23f == 9] <- NA

summary(NSL$qn23c) #2 NAs
#summary(NSL$qn23d) #92 NAs
summary(NSL$qn23e) #4 NAs
summary(NSL$qn23f) #13 NAs

#excluding qn23d
NSL <- NSL %>%
  mutate(discrimination = (qn23c + qn23e + qn23f))

summary(NSL$discrimination)
table(NSL$discrimination)
ggplot(NSL, aes(discrimination)) + 
  geom_histogram()

ggplot(NSL, aes(log(discrimination + 1))) + 
  geom_histogram()

log(.4 + 1)
```

Univariate Analyses: Outcome Variables: [Negative] Opinion of Trump
```{r}
table(NSL$qn14a)
table(NSL$qn17)

NSL$qn14a[NSL$qn14a == 8 | NSL$qn14a == 9] <- NA
NSL$qn17[NSL$qn17 == 8 | NSL$qn17 == 9] <- NA

NSL$qn14a[NSL$qn14a == 1] <- 0
NSL$qn14a[NSL$qn14a == 2] <- 1
summary(NSL$qn14a)

NSL$qn17[NSL$qn17 == 1] <- 0
NSL$qn17[NSL$qn17 == 2] <- 1
NSL$qn17[NSL$qn17 == 3] <- 0
NSL$qn17[NSL$qn17 == 4] <- 0.5
summary(NSL$qn17)

NSL <- NSL %>% 
  mutate(trump = (qn14a + qn17))
table(NSL$trump)
ggplot(NSL, aes(trump)) + 
  geom_bar()
```

Univariate Analyses: Outcome Variables: Political Party
```{r}
table(NSL$party)
NSL$party <- as.factor(NSL$party)
levels(NSL$party)[levels(NSL$party)=="1"] <- "Republican"
levels(NSL$party)[levels(NSL$party)=="2"] <- "Democrat"
levels(NSL$party)[levels(NSL$party)=="3"] <- "Independent"
levels(NSL$party)[levels(NSL$party)=="4"] <- "Ambivalent" #No preference
levels(NSL$party)[levels(NSL$party)=="5"] <- NA #Other party
levels(NSL$party)[levels(NSL$party)=="8"] <- "Ambivalent" #Don’t know
levels(NSL$party)[levels(NSL$party)=="9"] <- NA #Refused
table(NSL$party)
prop.table(table(NSL$party))

ggplot(NSL, aes(party)) + 
  geom_bar() + 
  labs(title = "Political Party", subtitle = "In politics today, do you consider yourself a Republican, Democrat, or Independent?", x = "Response", y = "Count")
```

Univariate Analyses: Outcome Variables: [Conservative] Immigration Policy Stance -- right skew
higher numbers indicate a more conservative stance
```{r}
summary(NSL$qn28)
summary(NSL$qn29)
#summary(NSL$qn31) #excluded from analyses

NSL$qn28[NSL$qn28 == 8 | NSL$qn28 == 9] <- NA
NSL$qn29[NSL$qn29 == 8 | NSL$qn29 == 9] <- NA
#NSL$qn31[NSL$qn31 == 8 | NSL$qn31 == 9] <- NA

NSL$qn28[NSL$qn28 == 1] <- 0
NSL$qn28[NSL$qn28 == 2] <- 1

NSL$qn29[NSL$qn29 == 2] <- 0

#NSL$qn31[NSL$qn31 == 2] <- 0
#NSL$qn31[NSL$qn31 == 3] <- 0


# NSL <- NSL %>% 
#   mutate(immigration = (qn28 + qn29 + qn31))

NSL <- NSL %>%
  mutate(immigration = (qn28 + qn29))

summary(NSL$immigration)

ggplot(NSL, aes(immigration)) + 
  geom_bar()
```

Cleaning the Dataset
```{r}
sample_NSL <- NSL %>% 
  select(citizen = qn9, language = qnlan3, discrimination, trump, party, immigration)
#View(sample_NSL)
summary(sample_NSL)

aggregate(formula = sample_NSL$immigration ~ sample_NSL$citizen, FUN = length)

#observing the NA data
sample_NSL %>% 
  filter(is.na(citizen))
sample_NSL %>% 
  filter(is.na(language)) #mostly naturalized citizens, Independents/Democrats
sample_NSL %>% 
  filter(is.na(discrimination)) #mostly natural born citizens, Independents/Democrats, negative opinions of trump
sample_NSL %>% 
  filter(is.na(trump))
sample_NSL %>%
  filter(is.na(party))
sample_NSL %>% 
  filter(is.na(immigration))

#making a dataset with no missing data
NSL_clean <- sample_NSL %>% 
  drop_na()

summary(NSL_clean)
write.csv(NSL_clean, file = "NSL_clean")
```
