---
title: "All_Work.Rmd"
author: "Leo Costa"
date: "12/14/2021"
output: html_document
---

```{r, include = false}
library(tidyverse)
library(dplyr)
library(haven)
library(parsnip)
library(nnet)

NSL <- read_sav("NSL.sav")
#View(NSL)
#names(NSL)
```

Univariate Analyses: Predictor Variables: Citizenship Status
```{r}
summary(NSL$qn9)
table(NSL$qn9)
NSL$qn9[is.na(NSL$qn9)] <- 3
NSL$qn9[NSL$qn9 == 9] <- NA

NSL$qn9 <- as.factor(NSL$qn9)
levels(NSL$qn9)[levels(NSL$qn9)=="1"] <- "Naturalized Citizen"
levels(NSL$qn9)[levels(NSL$qn9)=="2"] <- "Non-citizen"
levels(NSL$qn9)[levels(NSL$qn9)=="3"] <- "Natural Born Citizen"

table(NSL$qn9)
prop.table(table(NSL$qn9))

ggplot(NSL, aes(qn9)) + 
  geom_bar() + 
  labs(title = "Citizenship Status", subtitle = "Are you a citizen of the United States?", x = "Response", y = "Count")
```

Univariate Analyses: Predictor Variables: English Language Proficiency
lower numbers correspond to lower proficiency
```{r}
table(NSL$qnlan3) 

NSL$qnlan3 <- as.factor(NSL$qnlan3)
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="1"] <- "Proficient" #Very well
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="2"] <- "Proficient" #Pretty well
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="3"] <- "Not proficient" #Just a little
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="4"] <- "Not proficient" #Not at all
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="8"] <- NA
levels(NSL$qnlan3)[levels(NSL$qnlan3)=="9"] <- NA # 8: 2, 9: 3

summary(NSL$qnlan3)
prop.table(table(NSL$qnlan3))

ggplot(NSL, aes(qnlan3)) +
  geom_bar()
```

Univariate Analyses: Predictor Variables: Experiences of Discrimination - right skew
```{r}
NSL$qn23c[NSL$qn23c == 2] <- 0
NSL$qn23d[NSL$qn23d == 2] <- 0
NSL$qn23e[NSL$qn23e == 2] <- 0
NSL$qn23f[NSL$qn23f == 2] <- 0

table(NSL$qn23c) #8: 2 values
table(NSL$qn23d) #8: 2 values
table(NSL$qn23e) #8: 2 values; 9: 2 values 
table(NSL$qn23f) #8: 9 values; 9: 4 values
NSL$qn23c[NSL$qn23c == 8 | NSL$qn23c == 9] <- NA
NSL$qn23d[NSL$qn23d == 8 | NSL$qn23d == 9] <- NA
NSL$qn23e[NSL$qn23e == 8 | NSL$qn23e == 9] <- NA
NSL$qn23f[NSL$qn23f == 8 | NSL$qn23f == 9] <- NA

summary(NSL$qn23c) #2 NAs
#summary(NSL$qn23d) #92 NAs
summary(NSL$qn23e) #4 NAs
summary(NSL$qn23f) #13 NAs

#excluding qn23d
NSL <- NSL %>%
  mutate(discrimination = (qn23c + qn23e + qn23f))

summary(NSL$discrimination)
table(NSL$discrimination)
ggplot(NSL, aes(discrimination)) + 
  geom_histogram()

ggplot(NSL, aes(log(discrimination + 1))) + 
  geom_histogram()

log(.4 + 1)
```

Univariate Analyses: Outcome Variables: [Negative] Opinion of Trump
```{r}
table(NSL$qn14a)
table(NSL$qn17)

NSL$qn14a[NSL$qn14a == 8 | NSL$qn14a == 9] <- NA
NSL$qn17[NSL$qn17 == 8 | NSL$qn17 == 9] <- NA

NSL$qn14a[NSL$qn14a == 1] <- 0
NSL$qn14a[NSL$qn14a == 2] <- 1
summary(NSL$qn14a)

NSL$qn17[NSL$qn17 == 1] <- 0
NSL$qn17[NSL$qn17 == 2] <- 1
NSL$qn17[NSL$qn17 == 3] <- 0
NSL$qn17[NSL$qn17 == 4] <- 0.5
summary(NSL$qn17)

NSL <- NSL %>% 
  mutate(trump = (qn14a + qn17))
table(NSL$trump)
ggplot(NSL, aes(trump)) + 
  geom_bar()
```

Univariate Analyses: Outcome Variables: Political Party
```{r}
table(NSL$party)
NSL$party <- as.factor(NSL$party)
levels(NSL$party)[levels(NSL$party)=="1"] <- "Republican"
levels(NSL$party)[levels(NSL$party)=="2"] <- "Democrat"
levels(NSL$party)[levels(NSL$party)=="3"] <- "Independent"
levels(NSL$party)[levels(NSL$party)=="4"] <- "Ambivalent" #No preference
levels(NSL$party)[levels(NSL$party)=="5"] <- NA #Other party
levels(NSL$party)[levels(NSL$party)=="8"] <- "Ambivalent" #Don’t know
levels(NSL$party)[levels(NSL$party)=="9"] <- NA #Refused
table(NSL$party)
prop.table(table(NSL$party))

ggplot(NSL, aes(party)) + 
  geom_bar() + 
  labs(title = "Political Party", subtitle = "In politics today, do you consider yourself a Republican, Democrat, or Independent?", x = "Response", y = "Count")
```

Univariate Analyses: Outcome Variables: [Conservative] Immigration Policy Stance -- right skew
higher numbers indicate a more conservative stance
```{r}
summary(NSL$qn28)
summary(NSL$qn29)
#summary(NSL$qn31) #excluded from analyses

NSL$qn28[NSL$qn28 == 8 | NSL$qn28 == 9] <- NA
NSL$qn29[NSL$qn29 == 8 | NSL$qn29 == 9] <- NA
#NSL$qn31[NSL$qn31 == 8 | NSL$qn31 == 9] <- NA

NSL$qn28[NSL$qn28 == 1] <- 0
NSL$qn28[NSL$qn28 == 2] <- 1

NSL$qn29[NSL$qn29 == 2] <- 0

#NSL$qn31[NSL$qn31 == 2] <- 0
#NSL$qn31[NSL$qn31 == 3] <- 0


# NSL <- NSL %>% 
#   mutate(immigration = (qn28 + qn29 + qn31))

NSL <- NSL %>%
  mutate(immigration = (qn28 + qn29))

summary(NSL$immigration)

ggplot(NSL, aes(immigration)) + 
  geom_bar()
```

Cleaning the Dataset
```{r}
sample_NSL <- NSL %>% 
  select(citizen = qn9, language = qnlan3, discrimination, trump, party, immigration)
#View(sample_NSL)
summary(sample_NSL)

aggregate(formula = sample_NSL$immigration ~ sample_NSL$citizen, FUN = length)

#observing the NA data
sample_NSL %>% 
  filter(is.na(citizen))
sample_NSL %>% 
  filter(is.na(language)) #mostly naturalized citizens, Independents/Democrats
sample_NSL %>% 
  filter(is.na(discrimination)) #mostly natural born citizens, Independents/Democrats, negative opinions of trump
sample_NSL %>% 
  filter(is.na(trump))
sample_NSL %>%
  filter(is.na(party))
sample_NSL %>% 
  filter(is.na(immigration))

#making a dataset with no missing data
NSL_clean <- sample_NSL %>% 
  drop_na()

summary(NSL_clean)
write.csv(NSL_clean, file = "NSL_clean")
```

Bivariate Analyses: Multicollinearity
```{r}
#Citizenship Status (categorical) and English Language Proficiency (categorical)
NSL_clean %>%
  count(language, citizen) %>%
  group_by(language) %>%
  mutate(freq = n / sum(n))
#https://stackoverflow.com/questions/24576515/relative-frequencies-proportions-with-dplyr
ggplot(NSL_clean, aes(language, fill = citizen)) +
  geom_bar() +
  labs(title = "Relationship Between English Language Proficiency and Citizenship Status", y = "Count", x = "English Language Proficiency", fill = "Citizenship Status")

#English Language Proficiency (categorical) and Experiences of Discrimination (numerical)
ggplot(NSL_clean, aes(language, discrimination, color = language)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between English Language Proficiency and Experiences of\nDiscrimination", x = "English Language Proficiency", y = "Experiences of Discrimination")

#Experiences of Discrimination (numerical) and Citizenship Status (categorical)
ggplot(NSL_clean, aes(x = reorder(citizen, discrimination, FUN = median), y = discrimination, color = citizen)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between Experiences of Discrimination and Citizenship Status", x = "Citizenship Status", y = "Experiences of Discrimination")
```

Bivariate Analyses: [Negative] Opinion of Trump (numerical)
```{r}
#Citizenship Status (categorical)
NSL_clean %>% group_by(citizen) %>%
  summarize(median = median(trump, na.rm = TRUE),
            min = min(trump, na.rm = TRUE),
            max = max(trump, na.rm = TRUE),
            IQR = IQR(trump, na.rm = TRUE))
ggplot(NSL_clean, aes(citizen, trump, color = citizen)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between [Negative] Opinion of Trump and Citizenship Status", x = "Citizenship Status", y = "[Negative] Opinion of Trump")

#English Language Proficiency (categorical)
NSL_clean %>% group_by(language) %>%
  summarize(median = median(trump, na.rm = TRUE),
            min = min(trump, na.rm = TRUE),
            max = max(trump, na.rm = TRUE),
            IQR = IQR(trump, na.rm = TRUE))
ggplot(NSL_clean, aes(language, trump, color = language)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between [Negative] Opinion of Trump and English\nLanguage Proficiency", x = "English Language Proficiency", y = "[Negative] Opinion of Trump")

#Experiences of Discrimination (numerical)
cor(NSL_clean$trump, NSL_clean$discrimination, use = "complete.obs")
ggplot(NSL_clean, aes(trump, discrimination)) + 
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "Relationship Between [Negative] Opinion of Trump and Experiences of\nDiscrimination", x = "[Negative] Opinion of Trump", y = "Experiences of Discrimination")
```
Regression Model: [Negative] Opinion of Trump (numerical)
```{r}
NSL_clean$citizen <- relevel(NSL_clean$citizen, "Natural Born Citizen")

modelfit_trump_1 <- lm(formula = trump ~ citizen + language + discrimination, data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_trump_1)
summary(modelfit_trump_1)

modelfit_trump_2 <- lm(formula = log(3 - trump) ~ citizen + language + log(discrimination + 1), data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_trump_2)
summary(modelfit_trump_2)

modelfit_trump_3 <- lm(formula = log(3 - trump) ~ citizen + log(discrimination + 1), data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_trump_3)
summary(modelfit_trump_3)

AIC(modelfit_trump_1) #I was helping my friend with her own R project (for another class) and saw this is how she calculated AIC
AIC(modelfit_trump_2)
AIC(modelfit_trump_3)
```

Bivariate Analyses: Political Party (categorical)
```{r}
#Citizenship Status (categorical)
NSL_clean %>%
  count(party, citizen) %>%
  group_by(party) %>%
  mutate(freq = n / sum(n))
ggplot(NSL_clean, aes(party, fill = citizen)) +
  geom_bar() +
  labs(title = "Relationship Between Political Party and Citizenship Status", x = "Party", y = "Count", fill = "Citizenship Status")

#English Language Proficiency (numerical)
NSL_clean %>%
  count(party, language) %>%
  group_by(party) %>%
  mutate(freq = n / sum(n))
ggplot(NSL_clean, aes(party, fill = language)) +
  geom_bar() +
  labs(title = "Relationship Between Political Party and English Language Proficiency", x = "Political Party", y = "Count", fill = "English Language Proficiency")

#Experiences of Discrimination (numerical)
NSL_clean %>% group_by(party) %>%
  summarize(median = median(discrimination, na.rm = TRUE),
            min = min(discrimination, na.rm = TRUE),
            max = max(discrimination, na.rm = TRUE),
            IQR = IQR(discrimination, na.rm = TRUE))
ggplot(NSL_clean, aes(x = reorder(party, discrimination, FUN = median), y = discrimination, color = party)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between Political Party and Experiences of Discrimination", x = "Party", y = "Experiences of Discrimination")
```

Regression Model: Political Party (categorical) -- Multinomial Logistic Regression
```{r}
NSL_clean$party <- relevel(NSL_clean$party, "Independent")

modelfit_party_1 <- multinom_reg() %>% #specify model – logistic
  set_engine("nnet") %>% #computational engine – glm 
  set_mode("classification") %>% #specify mode – classification 	
	fit(party ~ citizen + language + discrimination, data = NSL_clean) #specify formula 
#https://parsnip.tidymodels.org/reference/multinom_reg.html 

modelfit_party_1

test1 <- multinom(party ~ citizen + language + discrimination, data = NSL_clean)
summary(test1)
test1_z <- summary(test1)$coefficients/summary(test1)$standard.errors
test1_p <- (1 - pnorm(abs(test1_z), 0, 1)) * 2
test1_p

test2 <- multinom(party ~ citizen + language + log(discrimination + 1), data = NSL_clean)
summary(test2)
test2_z <- summary(test2)$coefficients/summary(test2)$standard.errors
test2_p <- (1 - pnorm(abs(test2_z), 0, 1)) * 2
test2_p

AIC(test1)
AIC(test2)
```

Bivariate Analyses: [Conservative] Immigration Policy Stance (numerical)
```{r}
#Citizenship Status (categorical)
NSL_clean %>% group_by(citizen) %>%
  summarize(median = median(immigration, na.rm = TRUE),
            min = min(immigration, na.rm = TRUE),
            max = max(immigration, na.rm = TRUE),
            IQR = IQR(immigration, na.rm = TRUE))
ggplot(NSL_clean, aes(x = reorder(citizen, immigration, FUN = median), y = immigration, color = citizen)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between Citizenship Status and [Conservative] Immigration\nPolicy Stance", x = "Citizenship Status", y = "[Conservative] Immigration Policy Stance")

#English Language Proficiency (numerical)
NSL_clean %>% group_by(language) %>%
  summarize(median = median(immigration, na.rm = TRUE),
            min = min(immigration, na.rm = TRUE),
            max = max(immigration, na.rm = TRUE),
            IQR = IQR(immigration, na.rm = TRUE))
ggplot(NSL_clean, aes(language, immigration, color = language)) + 
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between [Conservative] Immigration Policy Stance and\nEnglish Language Proficiency", x = "English Language Proficiency", y = "[Conservative] Immigration Policy Stance")

#Experiences of Discrimination (numerical)
cor(NSL_clean$immigration, NSL_clean$discrimination, use = "complete.obs")
ggplot(NSL_clean, aes(immigration, discrimination)) + 
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "Relationship Between Experiences of Discrimination and [Conservative]\nImmigration Policy Stance", x = "Experiences of Discrimination", y = "[Conservative] Immigration Policy Stance")
```

Regression Model: [Conservative] Immigration Policy Stance (numerical)
```{r}
modelfit_immigration_1 <- lm(formula = immigration ~ citizen + language + discrimination, data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_immigration_1)
summary(modelfit_immigration_1)

modelfit_immigration_2 <- lm(formula = log(immigration + 1) ~ citizen + language + log(discrimination + 1), data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_immigration_2)
summary(modelfit_immigration_2)

modelfit_immigration_3 <- lm(formula = log(immigration + 1) ~ citizen + log(discrimination + 1), data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_immigration_3)
summary(modelfit_immigration_3)

AIC(modelfit_immigration_1)
AIC(modelfit_immigration_2)
AIC(modelfit_immigration_3)
```
