---
title: "Costa Final Project"
author: "Leo Costa"
date: "11/20/2021"
output: html_document
---

Bivariate Analyses: Multicollinearity
```{r}
#Citizenship Status (categorical) and English Language Proficiency (categorical)
NSL_clean %>%
  count(language, citizen) %>%
  group_by(language) %>%
  mutate(freq = n / sum(n))
#https://stackoverflow.com/questions/24576515/relative-frequencies-proportions-with-dplyr
ggplot(NSL_clean, aes(language, fill = citizen)) +
  geom_bar() +
  labs(title = "Relationship Between English Language Proficiency and Citizenship Status", y = "Count", x = "English Language Proficiency", fill = "Citizenship Status")

#English Language Proficiency (categorical) and Experiences of Discrimination (numerical)
ggplot(NSL_clean, aes(language, discrimination, color = language)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between English Language Proficiency and Experiences of\nDiscrimination", x = "English Language Proficiency", y = "Experiences of Discrimination")

#Experiences of Discrimination (numerical) and Citizenship Status (categorical)
ggplot(NSL_clean, aes(x = reorder(citizen, discrimination, FUN = median), y = discrimination, color = citizen)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between Experiences of Discrimination and Citizenship Status", x = "Citizenship Status", y = "Experiences of Discrimination")
```


Bivariate Analyses: [Negative] Opinion of Trump (numerical)
```{r}
#Citizenship Status (categorical)
NSL_clean %>% group_by(citizen) %>%
  summarize(median = median(trump, na.rm = TRUE),
            min = min(trump, na.rm = TRUE),
            max = max(trump, na.rm = TRUE),
            IQR = IQR(trump, na.rm = TRUE))
ggplot(NSL_clean, aes(citizen, trump, color = citizen)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between [Negative] Opinion of Trump and Citizenship Status", x = "Citizenship Status", y = "[Negative] Opinion of Trump")

#English Language Proficiency (categorical)
NSL_clean %>% group_by(language) %>%
  summarize(median = median(trump, na.rm = TRUE),
            min = min(trump, na.rm = TRUE),
            max = max(trump, na.rm = TRUE),
            IQR = IQR(trump, na.rm = TRUE))
ggplot(NSL_clean, aes(language, trump, color = language)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between [Negative] Opinion of Trump and English\nLanguage Proficiency", x = "English Language Proficiency", y = "[Negative] Opinion of Trump")

#Experiences of Discrimination (numerical)
cor(NSL_clean$trump, NSL_clean$discrimination, use = "complete.obs")
ggplot(NSL_clean, aes(trump, discrimination)) + 
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "Relationship Between [Negative] Opinion of Trump and Experiences of\nDiscrimination", x = "[Negative] Opinion of Trump", y = "Experiences of Discrimination")
```
Regression Model: [Negative] Opinion of Trump (numerical)
```{r}
NSL_clean$citizen <- relevel(NSL_clean$citizen, "Natural Born Citizen")

modelfit_trump_1 <- lm(formula = trump ~ citizen + language + discrimination, data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_trump_1)
summary(modelfit_trump_1)

modelfit_trump_2 <- lm(formula = log(3 - trump) ~ citizen + language + log(discrimination + 1), data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_trump_2)
summary(modelfit_trump_2)

modelfit_trump_3 <- lm(formula = log(3 - trump) ~ citizen + log(discrimination + 1), data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_trump_3)
summary(modelfit_trump_3)

AIC(modelfit_trump_1) #I was helping my friend with her own R project (for another class) and saw this is how she calculated AIC
AIC(modelfit_trump_2)
AIC(modelfit_trump_3)
```

Bivariate Analyses: Political Party (categorical)
```{r}
#Citizenship Status (categorical)
NSL_clean %>%
  count(party, citizen) %>%
  group_by(party) %>%
  mutate(freq = n / sum(n))
ggplot(NSL_clean, aes(party, fill = citizen)) +
  geom_bar() +
  labs(title = "Relationship Between Political Party and Citizenship Status", x = "Party", y = "Count", fill = "Citizenship Status")

#English Language Proficiency (numerical)
NSL_clean %>%
  count(party, language) %>%
  group_by(party) %>%
  mutate(freq = n / sum(n))
ggplot(NSL_clean, aes(party, fill = language)) +
  geom_bar() +
  labs(title = "Relationship Between Political Party and English Language Proficiency", x = "Political Party", y = "Count", fill = "English Language Proficiency")

#Experiences of Discrimination (numerical)
NSL_clean %>% group_by(party) %>%
  summarize(median = median(discrimination, na.rm = TRUE),
            min = min(discrimination, na.rm = TRUE),
            max = max(discrimination, na.rm = TRUE),
            IQR = IQR(discrimination, na.rm = TRUE))
ggplot(NSL_clean, aes(x = reorder(party, discrimination, FUN = median), y = discrimination, color = party)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between Political Party and Experiences of Discrimination", x = "Party", y = "Experiences of Discrimination")
```
Regression Model: Political Party (categorical) -- Multinomial Logistic Regression
```{r}
NSL_clean$party <- relevel(NSL_clean$party, "Independent")

modelfit_party_1 <- multinom_reg() %>% #specify model – logistic
  set_engine("nnet") %>% #computational engine – glm 
  set_mode("classification") %>% #specify mode – classification 	
	fit(party ~ citizen + language + discrimination, data = NSL_clean) #specify formula 
#https://parsnip.tidymodels.org/reference/multinom_reg.html 

modelfit_party_1

test1 <- multinom(party ~ citizen + language + discrimination, data = NSL_clean)
summary(test1)
test1_z <- summary(test1)$coefficients/summary(test1)$standard.errors
test1_p <- (1 - pnorm(abs(test1_z), 0, 1)) * 2
test1_p

test2 <- multinom(party ~ citizen + language + log(discrimination + 1), data = NSL_clean)
summary(test2)
test2_z <- summary(test2)$coefficients/summary(test2)$standard.errors
test2_p <- (1 - pnorm(abs(test2_z), 0, 1)) * 2
test2_p

AIC(test1)
AIC(test2)
```


Bivariate Analyses: [Conservative] Immigration Policy Stance (numerical)
```{r}
#Citizenship Status (categorical)
NSL_clean %>% group_by(citizen) %>%
  summarize(median = median(immigration, na.rm = TRUE),
            min = min(immigration, na.rm = TRUE),
            max = max(immigration, na.rm = TRUE),
            IQR = IQR(immigration, na.rm = TRUE))
ggplot(NSL_clean, aes(x = reorder(citizen, immigration, FUN = median), y = immigration, color = citizen)) +
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between Citizenship Status and [Conservative] Immigration\nPolicy Stance", x = "Citizenship Status", y = "[Conservative] Immigration Policy Stance")

#English Language Proficiency (numerical)
NSL_clean %>% group_by(language) %>%
  summarize(median = median(immigration, na.rm = TRUE),
            min = min(immigration, na.rm = TRUE),
            max = max(immigration, na.rm = TRUE),
            IQR = IQR(immigration, na.rm = TRUE))
ggplot(NSL_clean, aes(language, immigration, color = language)) + 
  geom_boxplot() + 
  geom_jitter(size = 1, alpha = .4) +
  theme(legend.position = "none") +
  labs(title = "Relationship Between [Conservative] Immigration Policy Stance and\nEnglish Language Proficiency", x = "English Language Proficiency", y = "[Conservative] Immigration Policy Stance")

#Experiences of Discrimination (numerical)
cor(NSL_clean$immigration, NSL_clean$discrimination, use = "complete.obs")
ggplot(NSL_clean, aes(immigration, discrimination)) + 
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "Relationship Between Experiences of Discrimination and [Conservative]\nImmigration Policy Stance", x = "Experiences of Discrimination", y = "[Conservative] Immigration Policy Stance")
```
Regression Model: [Conservative] Immigration Policy Stance (numerical)
```{r}
modelfit_immigration_1 <- lm(formula = immigration ~ citizen + language + discrimination, data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_immigration_1)
summary(modelfit_immigration_1)

modelfit_immigration_2 <- lm(formula = log(immigration + 1) ~ citizen + language + log(discrimination + 1), data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_immigration_2)
summary(modelfit_immigration_2)

modelfit_immigration_3 <- lm(formula = log(immigration + 1) ~ citizen + log(discrimination + 1), data = NSL_clean)
par(mfrow = c(2, 2))
plot(modelfit_immigration_3)
summary(modelfit_immigration_3)

AIC(modelfit_immigration_1)
AIC(modelfit_immigration_2)
AIC(modelfit_immigration_3)
```
